Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-02-11 analysis/paper/paper.Rmd
Forest plots with subsets as age

```{r figforestcofactors}
knitr::include_graphics("../../figFOREST.png")
```

>>>>

```{r figforestcofactors}
knitr::include_graphics("../figures/figForest.png")
```

```{r figforestcofactorskids}
knitr::include_graphics("../figures/kidsForest.png")
```

```{r figforestcofactorsadults}
knitr::include_graphics("../figures/adultsForest.png")
```
